\begin{recipe}[preparationtime={\unit[20]{min}},bakingtime={\unit[15]{min}},portion={6 paratha},source=\url{https://www.cookwithmanali.com/aloo-paratha/}]{Aloo Paratha}
\index{Indian}\index{Bread}\index{No Yeast}
\ingredients[17]{
2 & medium potatoes, boiled \\
\unit[\nicefrac{1}{4}]{tsp} & ajwain \\
1 & green chili, finely chopped \\
\unit[2]{tbsp} & finely chopped cilantro \\
\unit[\nicefrac{1}{4}]{tsp} & cumin powder \\
\unit[\nicefrac{1}{4}]{tsp} & garam masala \\
\unit[\nicefrac{1}{4}]{tsp} & amchur \\
\unit[\nicefrac{1}{8}-\nicefrac{1}{4}]{tsp} & chili powder (adjust to taste) \\
\unit[\nicefrac{3}{4}]{tsp} & salt (to taste) \\
\unit[3-4]{tsp} & oil or ghee (for cooking) \\
\textbf{Dough:} & \\
\unit[190]{g} & whole wheat flour \\
\unit[1]{tsp} & vegetable oil \\
\unit[\nicefrac{1}{4}]{tsp} & salt \\
& water}
\preparation{
\step Boil your potatoes if you haven't already. You can also do this in the Instant Pot on high for 8-10 minutes, depending on the size of your potatoes.
\step In a bowl mix together whole wheat flour (atta), oil and salt. Add water little by little and mix.
\step Knead to form a smooth and soft dough. Cover and let the dough rest for 15-20 minutes.
\step Divide the dough into 4-6 equal parts.
\step To make the filling, mash the boiled potatoes and transfer to a bowl.
\step Add chopped cilantro, salt, ajwain, chopped green chili, cumin powder, chat masala, garam masala powder, amchur and red chili powder.
\step Mix till everything is well combined. Adjust spice levels to taste if needed. The stuffing is now ready.
\step To make the paratha, take one of the dough balls and using your rolling pin roll it into a circle. Apply little oil (optional) all over the rolled dough.
\step Place 2-3 tablespoons of stuffing in the center. Don't overfill else it will be difficult to roll.
\step Bring all the edges together and pinch to seal the edges. Flatten the dough ball using your hands.
\step Now using your rolling pin, roll the dough to a circle of 7-8 inch diameter. The trick here is to apply equal pressure while rolling. If you do that, your paratha will turn round automatically.
\step Transfer the rolled paratha onto the hot tawa.
\step Cook the side for a minute or two and then flip over. Apply oil or ghee on the half-cooked side and flip again.
\step Now apply oil on the other side as well. Press with a spatula and cook the paratha till both sides have golden brown spots on them.
\step Repeat with the remaining dough balls.
}
\end{recipe}
