\begin{recipe}[portion={\unit[12]{tortillas}},source=\url{https://www.isabeleats.com/3-ingredient-authentic-mexican-corn-tortillas/}]{Corn Tortillas}        
	\ingredients[]{%
		\unit[2]{cups} & masa harina \\
		\unit[\nicefrac{2}{3}]{tsp} & salt \\
		\unit[1\nicefrac{1}{2}]{cups} & hot water \\
		\unit[1]{tsp} & olive oil \\
	}
	\preparation{%
		\step Mix the masa harina and salt in a large bowl.
		\step Pour the water and oil into the bowl, and mix until combined. Then form into a ball with your hands. The dough should be firm and springy when touched, if the mixture is too dry add more water in small amounts until the dough is springy and holds together.
		\step Place the ball in a bowl and cover. Let rest for 20 minutes.
		\step Divide the dough into 12 equal pieces, rolling each one into a ball and placing back into the covered container.
		\step Preheat a griddle over medium-high heat.
		\step Cut a gallon-sized ziploc bag on the sides, so it can open fully. Then place a ball inside the two halves and press down with a small casserole dish. You want it to be about \nicefrac{1}{8} inch thick.
		\step Place the tortilla on the hot griddle and cook for 20 seconds. Flip it over and cook for 20 more seconds.
		\step Flip again and cook for 40 more seconds or until it begins to bubble/puff. Flip again and cook until brown marks form.
		\step Remove the cooked tortilla and place in a kitchen towel inside of a large closable container to keep it warm and moist.
		\step Repeat for the remaining 11 tortillas.
	}
\end{recipe}        
