\begin{recipe}[preparationtime={\unit[3-4]{hrs}, depending on rise time},bakingtime={\unit[16-18]{min}},portion={6 buns},source=\href{https://www.youtube.com/watch/?v=gTGSUYMu6Ns}{Joshua Weissman}]{Fancy Burger Buns}
\index{Burger}\index{Bread}
	\ingredients[12]{%
		\unit[4]{tbsp} & milk \\
		\unit[2]{tbsp} & water \\
		\unit[20]{g} & bread flour \\
		\unit[\nicefrac{1}{2}]{cup} & milk \\
		\unit[1]{tbsp} & instant yeast \\
		\unit[320]{g} & bread flour \\
		\unit[1]{tsp} & salt \\
		\unit[35]{g} & sugar \\
		1 & egg \\
		1 & egg yolk \\
		\unit[3]{tbsp} & softened butter \\
		1 & egg \\
		splash & milk \\
	}
	\preparation{
		\step Combine the milk, water and bread flour in a small saucepan on medium-high heat and mix constantly until it comes together, this should happen quickly. It will begin to resemble a thick paste and no longer very liquidy.
		\step Warm the larger portion of milk to about 95\faren and combine with the yeast and let sit for 5-8 minutes.
		\step Combine the flour, sugar, and salt in the bowl of the stand mixer and whisk to combine.
		\step Using the dough-hook on low speed, add the yeast mixture and mix until combined. Then add in the sticky paste and mix until combined.
		\step Add the full egg and egg yolk while mixing on low speed.
		\step Increase the mixer speed to medium-low, and mix until everything is thoroughly combined. Scrape down the sides of the bowl intermittently.
		\step Gradually add the softened butter.
		\step Continue mixing for 3-5 minutes or until the dough is smooth.
		\step Make the dough into a large ball and place into a covered, greased bowl for 1-1.5 hours, or until doubled in size.
		\step Punch down the dough, then on a floured work surface, evenly divide the dough into 6 pieces.
		\step For each piece of dough, fold in the edges to make a more round dough then flip it over and pull it toward you. Then turn 90 degrees and pull again, repeating until the dough is a nice ball.
		\step Place all of the dough balls onto a sheet pan, with at least two inches between each ball. Cover with another tray, and let rise until doubled, 1.5-2 hours.
		\step Make an eggwash with the remaining milk and egg, then brush the top of the buns.
		\step Bake them at 375\faren for 16-18 minutes. Then brush them with melted butter afterwards, letting them cool on a wire rack.
	}
\end{recipe}
