\begin{recipe}[preparationtime={\unit[2.5-4]{hrs}, depending on rise time},bakingtime={\unit[15]{min}},portion={8 4-5 inch buns},source=\url{https://smittenkitchen.com/2009/07/light-brioche-burger-buns/}]{Light Brioche Burger Buns}
\index{Bread}\index{Burger}
\ingredients[11]{
\unit[1]{cup} + \unit[1]{tbsp} & water \\
\unit[3]{tbsp} & warm milk \\
\unit[2]{tsp} & active dry yeast \\
\unit[2\nicefrac{1}{2}]{tbsp} & sugar \\
2 & eggs \\
\unit[3]{cups} & bread flour \\
\unit[\nicefrac{1}{3}]{cup} & all-purpose flour \\
\unit[1\nicefrac{1}{2}]{tsp} & salt\\
\unit[2\nicefrac{1}{2}]{tbsp} & unsalted butter, softened\\
& sesame seeds (optional)
}
\preparation{
\step In a measuring cup, combine 1 cup warm water, milk, yeast, and sugar. Let stand until foamy, about 5 minutes. Meanwhile, beat 1 egg.
\step In a large bowl, whisk the flours with salt. Add the butter, divided into small pieces, and rub into the flower between your fingers, making crumbs.
\step Stir in yeast mixture and beaten egg and knead until smooth and elastic, 8-10 minutes. The dough will be on the sticky side, so it can be a bit messy. Try and leave the dough tackier than you would a round loaf.
\step Shape dough into a ball and return it to the bowl. Cover the bowl with plastic wrap or a towel and let rise in a warm place until doubled, 1-2 hours.
\step Line a baking sheet with parchment paper or a silicone baking mat. Divide the dough into 8 equal parts. Gently roll each into a ball and arrange 2-3 inches apart on the baking sheet. Cover loosely with plastic wrap or towel and let buns rise in a warm place for 1-2 hours.
\step Set a large shallow pan of water on the oven floor. Preheat oven to 400\faren with rack in center. Beat remaining egg with 1 tbsp water and brush on top of buns. Sprinkle with sesame seeds.
\step Bake buns, turning sheet halfway through, for about 15 minutes, until tops are golden brown. Transfer to a rack to cool completely.
}
\end{recipe}
