\begin{recipe}[preparationtime={\unit[30]{min} + \unit[45]{min} rise},bakingtime={\unit[15]{min}},portion={16 breadsticks},source=\href{https://www.foodnetwork.com/recipes/food-network-kitchen/almost-famous-breadsticks-recipe-1972945}{`Almost-Famous Breadsticks' from Food Network Magazine}]{Simple Breadsticks}
\index{Bread}
\ingredients[10]{
\unit[\nicefrac{1}{4} + 1\nicefrac{1}{4}]{cup} & warm water \\
\unit[2\nicefrac{1}{4}]{tsp} & dry active yeast \\
\unit[4\nicefrac{1}{4}]{cups} (560g) & all purpose flour \\
\unit[2]{tbsp} & sugar\\
\unit[1]{tbsp} & salt\\
\unit[2]{tbsp} & unsalted butter, softened\\
\unit[3]{tbsp} & unsalted butter, melted\\
\unit[\nicefrac{1}{2}]{tsp} & kosher salt \\
\unit{pinch} & garlic powder \\
\unit{pinch} & dried oregano
}
\preparation{
\step Place 1/4 cup warm water in the bowl of a mixer; sprinkle in the yeast and set aside until foamy, about 5 minutes. 
\step Add the flour, butter, sugar, fine salt and 1\nicefrac{1}{4} cups plus 2 tablespoons warm water; mix with the paddle attachment until a slightly sticky dough forms, 5 minutes. 
\step Knead the dough by hand on a floured surface until very smooth and soft, 3 minutes.
\step Roll into a 2-foot-long log; cut into 16 1\nicefrac{1}{2}-inch-long pieces.
\step Knead each piece slightly and shape into a 7-inch-long breadstick; arrange 2 inches apart on a parchment-lined baking sheet. Cover with a cloth; let rise in a warm spot until almost doubled, about 45 minutes. 
\step Preheat the oven to 400 \faren. Make the topping: Brush the breadsticks with 1\nicefrac{1}{2} tablespoons of the butter and sprinkle with \nicefrac{1}{4} teaspoon kosher salt. 
\step Bake until lightly golden, about 15 minutes. Meanwhile, combine the remaining \nicefrac{1}{4} teaspoon salt with the garlic powder and oregano.
\step Brush the warm breadsticks with the remaining 1\nicefrac{1}{2} tablespoons melted butter and sprinkle with the flavored salt.
}

\end{recipe}
