\begin{recipe}[source=\href{http://jgradspittsburgh.com/about/}{JGrads Pittsburgh},portion={2 Large Loaves}]{Sweet Challah}
\index{Jewish}\index{Bread}
	\ingredients[8]{%
		\unit[1\nicefrac{1}{2}]{tbsp} & active dry yeast \\
		\unit[2\nicefrac{1}{2}]{cups} & water \\
		\unit[150]{g} & sugar \\
		\unit[\nicefrac{1}{2}]{tbsp} & salt \\
		1 & egg \\
		\unit[\nicefrac{1}{2}]{cups} & oil \\
		\unit[1,040]{g} & all-purpose flour \\
		1 & egg \\
		splash & milk \\
	}
	\preparation{%
		\step Warm the water to about 90-95\faren (warm to the touch but you should be able to keep your finger in it for a moment).
		\step Combine the yeast and the water in the bowl of a stand mixer; mix to combine. No need to let the yeas mixture rise.
		\step Add the sugar, salt, eggs and oil. Mix until well combined.
		\step Using the dough hook attachment to mix, gradually add the flour until the dough is thick and only a little sticky.
		\step Grease a large bowl with some additional oil, then add the dough to the bowl. Flip the dough so it is well covered in oil. Let rise for about 1 hour or until doubled in size.
		\step Remove from the bowl and knead the dough on a lightly-floured surface (adding some flour if needed) until the dough is soft and not very sticky. Separate into two equal pieces.
		\step Working with one of the pieces, divide into 3 equal pieces and roll into long logs. Combine the logs at one end and press together to remove the seams, then braid the 3 pieces until there is nothing left to braid. Combine and press again to prevent unfolding.
		\step Repeat for the second loaf, then let the loaves rest for about 30 minutes.
		\step Combine the last egg and milk and scramble together to make an egg wash.
		\step Preheat the oven to 350\faren.
		\step Use a pastry bush to coat the top of the loaves with egg wash. At this point you can add whatever additional toppings you would like.
		\step Bake for 30-35 minutes, switching racks halfway through.
		\step Let cool on a wire cooling rack.
	}
\end{recipe}
