\begin{recipe}[preparationtime={\unit[2.5]{hours}},bakingtime={\unit[30-35]{minutes}},portion={2 loaves},source=\url{https://www.tasteofhome.com/recipes/basic-homemade-bread/}]{White Sandwich Bread}
\index{Bread}
\ingredients[8]{%
\unit[1]{cup} & water \\
\unit[2]{tsp} & active dry yeast \\
\unit[1]{cup} & milk \\
\unit[2]{tbsp} & butter \\
\unit[2]{tbsp} & sugar \\
\unit[1]{tbsp} & salt \\
\unit[715]{g} & all-purpose flour \\
& oil \\
}
\preparation{%
\step Mix the yeast, sugar and warm water(warm but should be able to keep a finger in it for a bit) in the bowl of the stand mixer. Let stand for about 5 minutes
\step Melt the butter and combine with the milk and salt. Add the mixture to the yeast mixture. Add 130 grams (1 cup) of the flour and mix until a clumpy mixture is formed.
\step Add the remaining 585 grams of flour to the stand mixture, gradually, mixing as you add. Mix unitl a shaggy, floury dough is formed.
\step Knead the dough for 8 to 10 minutes. Add flour if the dough is sticking to the sides of the bowl a tablespoon at a time. Dough should form a ball without sagging, and spring back when poked.
\step Grease a large bowl and transfer the dough to the greased bowl. Flip the dough ball so it is covered in oil. Cover and let rise in a warm place until doubled in size, about one hour.
\step Split the dough into two equal pieces and form each piece into a loose ball. Let rest for 10 minutes.
\step Grease 2 loaf pans. Smash a ball into a rectangle with the palms of your hand. Then fold the rectangle into overlapping thirds, pinch to close the sides and the ends. Fold in half by pressing down in the middle and bringing the sides together, pinch to close on the ends and side. Repeat for the second loaf.
\step Move the loaves to the loaf pans, by flipping them seam side down. Then let rest in a warm place until they start to dome over the sides of the pan, about an hour.
\step Heat the oven to 425 \faren. Slash the top of the loaves with a serated knife before you put them in the oven. When you add the loaves to the oven reduce the heat to 375\faren. Bake for 30 to 35 minutes. They should sound hollow when tapped.
\step Cool on a wire rack until completely cool before slicing.
}
\end{recipe}
