\begin{recipe}[source=\href{https://www.reddit.com/r/theppk/wiki/kitchen/favoriterecipes/seitanogreatness?utm_source=share\&utm\_medium=ios\_app\&utm\_name=iossmf}{Post Punk Kitchen Reddit}]{Seitan}
    \index{Chicken Wings}\index{Sandwich Meat}
	\ingredients{%
		\unit[180]{g} & vital wheat gluten \\
		\unit[\nicefrac{1}{4}]{cup} & nutritional yeast \\
		\unit[1]{tsp} & salt \\
		\unit[2]{tsp} & paprika \\
		\unit[\nicefrac{1}{4}]{tsp} & cinnamon \\
		\unit[\nicefrac{1}{4}]{tsp} & cumin \\
		\unit[1]{tsp} & black pepper \\
		\unit[\nicefrac{1}{8}]{tsp} & cayenne pepper \\
		\unit[1]{tsp} & garlic powder \\
		\unit[\nicefrac{3}{4}]{cup} & cold water \\
		\unit[4]{tbsp} & tomato paste \\
		\unit[2]{tbsp} & olive oil \\
		\unit[1]{tbsp} & soy sauce \\
		\unit[2]{tbsp} & worcestershire sauce \\
	}
	\preparation{%
		\step In a large bowl, combine all of the dry ingredients and mix well.
		\step In a separate medium bowl, combine all of the wet ingredients and mix well.
		\step Add the wet ingredients to the dry and stir until all of the dry material is incorporated.
		\step Turn out the bowl onto a clean surface and knead the dough until you are content.
		\step At this point you can shape the seitan into whatever shape you would like for your specific use (i.e. wings, log, small sausages, etc. )
		\step Preheat oven to 325\faren.
		\step If shaping into a large log, wrap the entire piece of dough with aluminum foil twisting the ends. Bake for 90 minutes and unwrap when done to fully cool.
		\step Alternatively, if making chkn wings then form into many small nuggets on a greased baking sheet. Bake for about 30 minutes, flipping once in the midway through.
	}
\end{recipe}
