\begin{recipe}[source=\url{https://sallysbakingaddiction.com/super-moist-carrot-cake/}]{Carrot Cake}
\index{Cake}
\ingredients[20]{%
\unit[200]{g} & brown sugar \\
\unit[\nicefrac{3}{4}]{cup} & vegetable oil \\
\unit[60]{g} & greek yogurt \\
3 & eggs \\
\unit[2]{tsp} & vanilla extract \\
\unit[250]{g} & all-purpose flour \\
\unit[1]{tsp} & baking soda \\
\unit[2]{tsp} & ground cinnamon\\
\unit[\nicefrac{1}{4}]{tsp} & ground nutmeg \\
\unit[\nicefrac{1}{2}]{tsp} & salt \\
\unit[2]{cups} or \unit[260]{g} & finely grated carrots\\
\unit[\nicefrac{3}{4}]{cup} & pecan pieces\\
\\
\unit[8]{oz} (224g) & cream cheese, room temp\\
\unit[\nicefrac{1}{2}]{cup} (115g) & unsalted butter, softened\\
\unit[240-300]{g} & confectioners' suger\\
\unit[2]{tbsp} & heavy cream\\
\unit[2]{tsp} & vanilla extract\\
& salt to taste
}
\preparation{
\step Preheat oven to 350 \faren (177 \degree C). Spray 9 or 10inch springform pan with nonstick cooking spray.
\step Set out the cream cheese for the frosting so it may soften as you make the cake batter.
\step In a large bowl with a handheld or stand mixer fitted with a paddle attachment on medium speed, combine the brown sugar and oil. Beat in the yogurt until fully combined – about 60 seconds. Mixture will be gritty and thick. 
\step Add the eggs, one at a time, beating well after each addition. Mix in the vanilla. Set aside.
\step In a separate bowl, combine the flour, baking soda, cinnamon, nutmeg, and salt. 
\step With a spatula, manually stir the dry ingredients into the wet ingredients until just combined and all flour pockets are gone – do not overmix. Fold in the finely shredded carrots and pecan pieces. Pour or spoon batter into prepared springform pan.
\step Bake cake for 32-38 minutes or until toothpick inserted in the center comes out clean. Do not overbake, which will dry out cake. Check the cake at 30 minutes, then again at 32. Allow cake to cool completely before frosting.
\step To make the frosting, beat the softened cream cheese and butter together on medium speed for 2-3 minutes until soft, creamy, and combined thoroughly.
\step Add 2 cups of powdered sugar and beat until thick and combined. Add 2 Tablespoons heavy cream and 2 teaspoons vanilla extract. Beat on medium speed for 2 more minutes.
\step Add more powdered sugar until desired thickness is reached. Add salt to taste. 
}
\hint{
This recipe also can be made into 12 cupcakes. Bake time is 17-18 minutes.
}
\end{recipe}
