\begin{recipe}[source={Mom},bakingtime={\unit[65]{min}},portion={\unit[1]{loaf}}]{Chocolate Chip Banana Bread}
	\ingredients[10]{%
		\unit[\nicefrac{1}{2}]{cup} & butter \\
		\unit[334]{g} & sugar \\
		2 & eggs \\
		\unit[\nicefrac{1}{4}]{tsp} & salt \\
		\unit[1\nicefrac{1}{2}]{tsp} & baking powder \\
		\unit[\nicefrac{1}{2}]{tsp} & baking soda \\
		\unit[\nicefrac{1}{4}]{cup} & sour cream \\
		2-3 & bananas \\
		\unit[260]{g} & flour \\
		\unit[1]{tsp} & vanilla extract \\
		\unit[1]{cup} & chocolate chips \\
	}
	\preparation{%
		\step In the bowl of a stand mixer, cream together the butter and sugar.
		\step Preheat the oven to 350\faren
		\step While the sugar and butter are creaming together, dissolve the baking powder and baking soda into the sour cream and let sit until it starts to fluff.
                \step After the butter and cream are creamed and the sour cream is fluffy, add the salt and eggs and mix until combined.
		\step Add the sour cream to the stand mixer once it has fluffed.
		\step Peel the bananas, slightly mash, then mix in with the contents of the stand mixer.
		\step Gradually add the flour to the bowl of the stand mixer while mixing.
		\step Add the vanilla extract and chocolate chips, mix until the chocolate chips are thoroughly mixed in.
		\step Pour the mixture into a bread loaf pan.
		\step Bake for 65 minutes.
		\step Remove from loaf pan once slightly cool, then move to a cooling rack. The bread tastes great fresh or can be frozen and reheated later.
	}
\end{recipe}
