\begin{recipe}[source=\url{https://www.deliciousmagazine.co.uk/recipes/the-best-sticky-toffee-pudding/},portion={\unit[8]{portions}},preparationtime={\unit[30]{min}},bakingtime={\unit[50]{min}}]{Sticky Toffee Pudding}
\ingredients[27]{
        \unit[160]{g} & whole dates, stoned and roughly chopped \\
        \unit[150]{ml} & boiling water \\
        \unit[1]{tsp} & vanilla extract \\
        \unit[90]{g} & unsalted butter, softened \\
        \unit[150]{g} & light muscovado (or light brown) sugar \\
        2 & large eggs \\
        \unit[2]{tbsp} & black treacle (or molasses) \\
        \unit[175]{g} & self-raising flour \\
        \unit[1]{tsp} & baking soda \\
        \unit[100]{ml} & whole milk \\
                       & \\
        \multicolumn{2}{l}{\large Toffee Sauce} \\[0.2cm]
        \unit[225]{g} & light muscovado (or light brown) sugar \\
        good slug & brandy or rum \\
        \unit[100]{g} & unsalted butter, softened \\
        \unit[275]{ml} & double (or heavy) cream \\
        \unit[1]{tbsp} & black treacle (or molasses)
}
\preparation{
        \step Put the dates in a mixing bowl with the water. Leave for 30 minutes until cool, then mash with a fork to a rough pulp. Stir through the vanilla and set aside. Butter a 8x8 dish and set aside. Heat the oven to 335\faren/fan 300\faren.
        \step While the dates are soaking, use an electric mixer or wooden spoon to beat the 90g butter and 150g sugar until light and creamy. Add the eggs one at a time, beating well before adding the next. Beat in the black treacle, then mix the flour with the bicarb and gently fold in one third using a metal spoon or balloon whisk. Fold in a third of the milk, then repeat until all the flour and milk are used up. Stir the soaked dates, with their liquid, into the batter – it may curdle, but don’t worry. Spoon into the prepared dish.
        \step Bake for 50 minutes or until the pudding is risen and firm, and a skewer pushed into the middle comes out clean (cover with foil after 40 minutes if the edges are browning too much). If the skewer comes out with what looks like uncooked mixture on it, it might be a piece of date. Taste it – if you can taste uncooked flour it will need longer.
        \step Meanwhile, make the toffee sauce. Put the 225g sugar, brandy, 100g butter and half the cream in a large, heavy-based pan and heat gently. When the sugar has dissolved, turn up the heat, stir in the treacle and bubble, stirring, for 2-3 minutes until the mix is a rich toffee colour. Take the pan off the heat and stir in the rest of the cream. Keep warm.
        \step Leave the pudding to cool for 20 minutes, then skewer it all over and pour over half the sauce. Leave for another 15 minutes, then serve drizzled with the rest of the sauce, with our toasted nut and demerara ice cream, if you like.
}
\hint{
        \begin{itemize}
                \item \unit[175]{g} self-raising flour = \unit[175]{g} all-purpose flour + \unit[2]{tsp} baking soda + \unit[1]{tsp} salt
                \item You can substitute any other milk for the whole milk.
        \end{itemize}
}
\end{recipe}
