\begin{recipe}[preparationtime={\unit[10]{min}},bakingtime={\unit[20]{min}},source=\url{https://www.makingthymeforhealth.com/vegan-avocado-brownies/}]{Vegan Avocado Brownies}
\index{Brownie}\index{Vegan}\index{Chocolate}\index{Avocado}
\ingredients[]{
\nicefrac{1}{2} & medium ripe avocado \\
\unit[1]{cup} + \unit[2]{tbsp} & plant-based milk \\
\unit[\nicefrac{1}{4}]{cup} & maple syrup \\
\unit[\nicefrac{1}{2}]{cup} & sugar \\
\unit[1]{cup} & all-purpose flour \\
\unit[\nicefrac{1}{2}]{cup} & unsweetened cocoa powder \\
\unit[1]{tsp} & baking soda \\
\unit[\nicefrac{1}{2}]{tsp} & salt \\
\unit[\nicefrac{1}{2}]{cup} & chocolate chips
}
\preparation{
\step Preheat the oven to 350\faren. Lightly grease an 8x8" baking dish.
\step In a blender, combine the avocado, soymilk, maple syrup and sugar. Blend for about 15-20 seconds, until smooth.
\step In a large bowl, combine the flour, cocoa powder, baking soda, and salt then stir together. 
\step Pour the wet ingredients in the blender into the bowl with the dry. Stir until combined. Then add the chocolate chips and mix until they are evenly distributed.
\step Bake in the oven for 15-20 minutes, until set. You should be able to stick a fork in the center and have it come out clean.
\step Allow to cool for at least 15 minutes before serving.
}

\hint{
\begin{itemize}
    \item You can substitute the flour for whole-wheat flour if desired. 
    \item Feel free to add walnuts or any other type of nut else to this recipe!
\end{itemize}
}
\end{recipe}
