\begin{recipe}[preparationtime={\unit[15]{minutes}},bakingtime={\unit[20]{minutes}},source=\url{https://www.mexicoinmykitchen.com/pasta-with-creamy-roasted-poblano-sauce/}]{Creamy Roasted Poblano Pasta}
\index{Mexican}\index{Pasta}\index{Vegetarian}
	\ingredients[9]{%
		\unit[1]{package} & spaghetti or other pasta\\
		\unit[6]{large} & poblano peppers \\
		\unit[1]{cup} & onion \\
		\unit[2]{cloves} & garlic \\
		\unit[1]{cup} & milk \\
		\unit[1\nicefrac{1}{2}]{cup} & heavy cream \\
		\unit[4]{tsp} & bouillon \\
		\unit[1\nicefrac{1}{2}]{cup} & corn \\
	}
	\preparation{%
		\step Roast the poblano peppers (can be done over the gas stove or in a pan). Then peel and devein the peppers (peeling is made easier when they are more charred).
		\step Cook the pasta according to the package instructions. Drain and set aside until the sauce is ready.
		\step Heat 1 tablespoon of oil in a skillet over medium heat, add the onion. Cook for about 2 minutes then add the garlic. Continue cooking until the onion is transparent.
		\step Place the roasted poblanos, cream, milk and bouillon into a blender. Blend until smooth (Note: if using heavy cream then it may form curds in the blender, but these will melt when warmed later)
		\step Add the sauce to the skillet and cook on low for about 6 minutes.At this point you can add the corn and any other veggies. Stir frequently.
		\step Combine the pasta and sauce. Enjoy!
	}
	\hint{
		Instead of heavy cream you can use mexican cream, sour cream, or cream cheese. You just need some sort of cream.
	}
\end{recipe}
