\begin{recipe}[source=adapted from \href{https://www.eatingthaifood.com/thai-larb-recipe/}{Mark Wiens} and \href{https://thewoksoflife.com/mushroom-larb/}{The Woks of Life}]{Vegetarian Larb}
        \index{Thai}\index{Vegetarian}
	\ingredients[23]{%
        \multicolumn{2}{l}{\large Pre-ingredient}\\[0.2cm]
        \unit[1\nicefrac{1}{2}]{tbsp} & uncooked sticky rice (or more, see hint) \\
                                      & \\
        \multicolumn{2}{l}{\large Main ingredients}\\[0.2cm]
        \unit[1]{lb} & mushrooms or tofu, finely chopped or crumbled (see recipe) \\
        \unit[\nicefrac{1}{2}]{tbsp} & chili flakes or powder \\ 
        \unit[\nicefrac{1}{8}]{tbsp} & sugar (just a pinch) \\
        \unit[\nicefrac{1}{2}]{tbsp} & fish sauce \\
        1.5 & limes, juiced \\
        1-2 & shallots, thinly sliced \\
        3-5 & spring onions, chopped \\
        around 20 & leaves of fresh mint \\
        a few & cilantro (or long coriander) leaves, optional \\
        some  & Thai sweet basil, for garnish
	}

	\preparation{%
            \step First step is to make the toasted rice. Heat a frying pan on low heat, toss in the uncooked sticky rice (no oil). Stir continuously, kind of like you’re roasting peanuts or coffee. Toast the rice until it turns from white to golden yellow, almost to the point where it looks like brown wheat. It will also be very fragrant and smell almost like popcorn. This will take around 15 minutes.
            \step Once the rice is finished toasting, and has cooled off a bit, put it into your stone mortar and pestle. Pound the rice until it turns into a coarse powder (a blender or food processor will also work fine). Put your toasted sticky rice powder in a bowl aside. You will use about \textbf{1 heaping tablespoon} in the main recipe.
            \step Add oil to a wok/large pan, and stir-fry your mushrooms or tofu. You can use either of these ingredients or both. The goal is to get a similar texture to ground pork (what is used traditionally). Oyster or shiitake mushrooms work great, but normal cremini mushrooms are fine too. If you use both mushrooms and tofu, put in the tofu first, as that will take longer to brown. Stir-fry until they are browned on the edges.
            \step Add 1 heaping tablespoon of your toasted rice powder to your mushrooms/tofu. Also toss in your chili flakes/powder.
            \step Add sugar, fish sauce, lime juice, and stir.
            \step Add your shallots, spring onions, and mint leaves, and give the larb a good mix.
            \step Taste test. See if it needs more fish sauce for saltiness, lime juice, or chili flakes.
            \step Dish it out onto a plate and garnish with more mint leaves, Thai sweet basil, and cilantro.
	}

	\hint{
        \begin{itemize}
                \item You can make more toasted rice powder than you need for the next time you make this!
                \item You can use fresh chilis for the spice instead of chili powder/flakes.
                \item If you want to make this completely vegan, you can use vegan fish sauce, or soy sauce in a pinch. 
        \end{itemize}
}
\end{recipe}        
