\begin{recipe}[
	]{Baingan Masala (Spicy Eggplant Curry)}\index{Indian}\index{Spicy}\index{Eggplant}
\ingredients[20]{%
	plenty of & oil\\
	\unit[\nicefrac{1}{4}]{tsp} & garlic powder \\
	\unit[\nicefrac{1}{4}]{tsp} & onion powder \\
	4 & green chilies \\
	\unit[2]{tbsp} (\unit[22]{g}) & ginger \\
	\unit[\nicefrac{3}{4}]{tsp} & turmeric powder \\
	5 & tomatoes \\
	\unit[3]{tsp} & coriander powder \\
	\unit[3]{tsp} & kashmiri chili powder\\
	\unit[3]{tbsps} & shredded coconut \\
	\unit[2]{tsp} (divided)& salt \\
	\unit[800]{g} & eggplant \\
	\unit[1\nicefrac{1}{2}]{tsp} & cumin seeds\\
	\unit[1]{tsp} & mustard seeds\\
	3 & bay leaves \\
	1 & cinnamon stick \\
	\unit[2]{cups} & water \\
	\unit[\nicefrac{3}{4}]{tsp} & garam masala \\
	\unit[4-5]{sprigs} & cilantro (coriander) leaves \\
}
\preparation{
	\step Heat 5-7 tablespoons oil in a large pan on medium-high heat.
	\step Chop up the ginger into small pieces. Cut the tomatoes into large pieces.
	\step Add the garlic powder, onion powder, green chilies, chopped ginger, turmeric, and tomatoes to the pan. Mix well and saute for 1 minute.
	\step Add the coriander powder, chili powder, and shredded coconut. Mix in and saute for 1 minute. Put heat on low and cover for 2 minutes.
	\step Add 1 teaspoon of salt and mix well. Remove the pan from the stove and set aside to cool.Once the mixture is cool enough, blend it into a smooth paste.
	\step Cut the eggplant up into large cubes (or cut Xs into the bottoms of small eggplants all the way to the stem).
	\step Heat deep frying oil on medium to high heat. (Also now is a good time to pressure cook some rice)
	\step Gently add the eggplant to boil (Don't splash the oil!).
	\step Deep fry for 3-4 minutes, or until soft, stirring after 1 minute and flipping occasionally for even cooking. Set aside on paper towels to drain oil. 
	\step Heat 4-5 tablespoons oil on high heat. Add the cumins seeds, mustard seeds, bay leaves, and cinnamon stick. Saute untill fragrant (the mustard seeds popping is normal, but don't let it go too crazy). 
	\step Add the blended paste (be careful it will probably splash a bit), and add about 1 teaspoon salt, or to taste and mix well.
	\step Stir until the mixture begins to bubble. Lower the heat and cover. Let simmer for about 6 minutes.
	\step Add the water to the blender (gotta clean out all of the yummy paste) to rinse it off.
	\step Add the blender water to the stove and mix well. Bring the mixture to a boil. Lower the heat a bit and let simmer for 3 minutes with the lid on.
	\step Add the fried eggplants and mix well. Set the heat to medium, cover with a lid and cook for 5 minutes.
	\step Add the garam masala and cilantro leaves, mix well. Enjoy!
}
\suggestion{
	\begin{itemize}
		\item You can add 4 dried kashmiri chilies at the beginning if you want extra heat, but the 4 green chilies are plenty
		\item Instead of the 5 tomatoes you can use 600 grams crushed tomatoes. Then you can avoid cutting up the tomatoes!
	\end{itemize}
}
\end{recipe}
